---
title: "Corona Virus Report"
author:
- familyname: XXXX
  othernames: XXX
  address: Monash Universtidy
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries

library(tidyverse)
library(readr)
library(kableExtra)
library(bookdown)

```



<<<<<<< HEAD
\section*{Country XX1 and YY1"}

\section*{Country XX2 and YY2}

library(readr)
worldwidecases <- read_csv("Data/worldwidecases.csv")
View(worldwidecases)

```{r}
Brazil <- worldwidecases %>% 
  filter(countriesAndTerritories == "Brazil")

unique(worldwidecases$countriesAndTerritories)

France <- worldwidecases %>% 
  filter(countriesAndTerritories == "France")

```


=======
\section*{Country XX1 and YY1}

```{r ,warning=FALSE,message=FALSE}
worldwide_cases <- read_csv("data/worldwidecases.csv")
```
```{r ,warning=FALSE,message=FALSE}
barbados_cases <- worldwide_cases %>%
  filter(countriesAndTerritories=="Barbados") %>%
  group_by(month,year) %>%
  summarise(n = sum(cases))

barbados_cases %>%
  ggplot(aes(x=month,y=n)) + geom_line()
```
This is the data

\section*{Country XX2 and YY2}
>>>>>>> smriti

\section*{Country XX3 and YY3}



